---
title: "Hello R"
author: "Quang Le"
date: 2/12/2025
output: html_document

---

### Load packages

```{r load-packages, message=FALSE}
library(tidyverse) 
library(datasauRus)
```

### Exercise 1

*In this Exercise, the datasauRus has:*

-   1846 rows,
-   3 columns **(including dataset, x, and y values)**
    -   *dataset:* this column shows where the entries are form.
    -   *x:* it represents x values.
    -   *y:* it represents y values.

### Exercise 2

*First let's plot the data in the dino dataset:*

```{r plot-dino, fig.height=3, fig.width=6}
dino_data <- datasaurus_dozen %>%
  filter(dataset == "dino")
ggplot(data = dino_data, mapping = aes(x = x, y = y)) +
  geom_point()
```

*And next calculate the correlation between `x` and `y` in this dataset:*

```{r cor-dino}
dino_data %>%
  summarize(r = cor(x, y))
```

*Answer:* **r_dino = -0.0645**

### Exercise 3

*First of all, let's plot the data in the star data set:*

```{r plot-star}
star_data <- datasaurus_dozen %>%
  filter(dataset == "star")
ggplot(data = star_data, mapping = aes(x = x, y = y))+ 
  geom_point()  
```

*Next, calculate the correlation between x and y in this data set:*

```{r cor-star}
star_data %>%
  summarise(r_star = cor(x, y))
```

*Answer:* **r = -0.0630**

> **Comparison** **the difference value between *r_star* and *r_dino.***

| **r_star** | **r_dino** | **The difference**                                 |
|--------------|--------------|--------------------------------------------|
| *-0.063*   | *-0.0645*  | *star data is .0015 higher than that of dino data* |

### Exercise 4

*First step: Let's plot the data in the circle data set:*

```{r plot-circle}
circle_data <- datasaurus_dozen %>% 
  filter(dataset == "circle")
ggplot(data = circle_data, mapping = aes(x = x, y = y)) +
  geom_point()
```

*Next step is check for unique values in the data columns. When filter the "circle", a star was shown accidentally.*

*Note:* It can be fixed after pasting code from Exercise 3 to Exercise 4 by editing the argument data = star_data in lieu of circle_data.

```{r check variable-uniques}
unique_values <- unique(dino_data$dataset)

#Print the unique values
print(unique_values)
```

*Then, calculate the correlation between x and y in the data set:*

```{r cor-circle}
circle_data %>% 
  summarise(r_circle = cor(x,y))
```

*Answer:* **r_circle = -0.0683**

> **Comparison *the diffrence between r_circle and r_dino***

> | **r_cirle** | **r_dino** | **The difference**                          |
> |-------------|------------|---------------------------------------------|
> | -0.0683     | -0.0645    | *circle is 0.0038 lower than that of dino.* |

> ### Exercise 5

*Final step: Plot all data st at once.*

```{r plot-faucet}
ggplot(datasaurus_dozen, aes(x = x, y = y, color = dataset)) + geom_point()+ 
  facet_wrap(~ dataset, ncol = 3) +
  theme(legend.position = "none")
```

*After that, utilize the 'group_by' function to generate all the summary of correlation coefficients.*

```{r cor-summary}
datasaurus_dozen %>%
  group_by(dataset) %>%
  summarise(r = cor(x, y))
```
