---
title: "Hello R"
author: "Quang Le"
date: "DATA 2401 - `r format(Sys.time(), '%d %B, %Y'`"
output: html_document
---

### Load packages

```{r load-packages, message=FALSE}
library(tidyverse) 
library(datasauRus)
```

### Exercise 1

*In this Exercise, the dino_data has:*

-   142 rows,
-   3 columns **(including dataset, x, and y values)**
    -   *dataset:* this column shows where the entries are form.
    -   *x:* it represents x values.
    -   *y:* it represents y values.

### Exercise 2

*First let's plot the data in the dino dataset:*

```{r plot-dino, fig.height=3, fig.width=6}
dino_data <- datasaurus_dozen %>%
  filter(dataset == "dino")
ggplot(data = dino_data, mapping = aes(x = x, y = y)) +
  geom_point()
```

*And next calculate the correlation between `x` and `y` in this dataset:*

```{r cor-dino}
dino_data %>%
  summarize(r = cor(x, y))
```

*Answer:* **r_dino = -0.0645**

### Exercise 3

*First of all, let's plot the data in the star data set:*

```{r plot-star}
star_data <- datasaurus_dozen %>%
  filter(dataset == "star")
ggplot(data = star_data, mapping = aes(x = x, y = y))+ 
  geom_point()  
```

*Next, calculate the correlation between x and y in this data set:*

```{r cor-star}
star_data %>%
  summarise(r_star = cor(x, y))
```

*Answer:* **r = -0.0630**

> **Comparison**

| **r_star** | **r_dino** | **The difference**                                 |
|------------|------------|----------------------------------------------------|
| *-0.063*   | *-0.0645*  | *star data is .0015 higher than that of dino data* |

### Exercise 4

*First step: Let's plot the data in the circle data set:*

```{r plot-circle}
circle_data <- datasaurus_dozen %>% 
  filter(dataset == "circle")
ggplot(data = circle_data, mapping = aes(x = x, y = y)) +
  geom_point()
```

```{r}


```

### Exercise 5

(Add code and narrative as needed. To add R chunks either type out the backticks, curly braces, and the letter `r` or use the Insert chunk button above, with the green +C.)
